\documentclass[10pt,a4paper,twoside,openany,hidelinks]{book}

%JAPANESE
\usepackage{fontspec}
\defaultfontfeatures{Ligatures={NoCommon, NoDiscretionary, NoHistoric, NoRequired, NoContextual}}
\setmainfont{CMU Serif}
\usepackage{xeCJK}
\xeCJKsetup{CJKmath=true}
\setCJKmainfont{MS Mincho} % or some other Japanese font

\usepackage{maths}
\usepackage{stylish}

\usepackage{tkz-graph}
\GraphInit[vstyle = Shade]

\title{D\&D Notes}
\date{\today}

\usepackage{lipsum}
\usepackage{stmaryrd}

\tikzset{EdgeStyle/.style   = {thick,
                               double          = orange,
                               double distance = 1pt}}

\tikzset{
    labl0/.style={anchor=south, rotate=-30, inner sep=.5mm}
}

\tikzset{
    labl1/.style={anchor=south, rotate=30, inner sep=.5mm}
}

\tikzset{
    labl2/.style={anchor=south, rotate=60, inner sep=.5mm}
}

\tikzset{
    labl3/.style={anchor=south, rotate=90, inner sep=.5mm}
}

\tikzset{
    labl4/.style={anchor=south, rotate=-90, inner sep=.5mm}
}

\newcommand{\from}{\leftarrow}

\usepackage[nottoc]{tocbibind}

\begin{document}

\maketitle

\mainmatter

\chapter*{Session 3}

The group writes a note to the hobgoblin that says that they should look for the cave with the buttons and that we left doors open.


They decide to go towards the tower through the plains. After about 15 minutes they figure out that the tower is at least 50 meters tall, possibly more.
It's sort of dark yellow, and a bit less than 70 meter tall if it's a few hours walk.

They go through muddy ground, not quicksand, and see at some point a diagonal trail of animals, walking steadily through the mud. There are multiple types of traces.

They see those within 500 meters or so, and they walk away. Kortarr sees large animals, bigger than usual cows and with lots of fur. It seems that the animals eat something from the ground, and also the ground itself.
One of them raises its head and looks at them. It has protruding teeth and a grey face. It examines Kortarr while walking. It has a green bump over the eye. We don't know how many legs they have or look at their legs since they're covered with fur.
Sunset is nigh and it gets colder.

As they get closer they see the tower is at least 100 meters tall. They see some of the sky through the pores at the sides of the tower. The radius is approximately 20 meters. They're about third of way through. They set for the night after drying the earth. They see worms in the earth, possibly part of what the cow-like animals ate.

First, Chattaan and Aio guard the camp. They hear voices that sound like animals, from a few directions. They sound like different types of animals, somewhat dog-like and it seems like they communicating with each other. It's hard to approximate the distance of the sound, but it seems like it's not from very near.
Then Kortarr takes his turn to guard. He approximates the nearest creatures are to the left-back from the tower, but can't say whether the distance of the nearest creatures is 400 meters or 5 kilometers.

Fechin then takes his turn, and notices after two hours or so creatures, bearing weapons, approaching. About 7 gnolls (humanoids and canine-like), very twisted: One has two heads, one has a tail, one has horns like those of cow-like creatures, one has bigger front legs.

After fighting the gnolls, and leaving all of them but one to bite the dust, the group captures the last of them. Some of the killed gnolls seem to be undead and move a bit, but aren't a cause for fear. After a short rest, during which the cow-like creatures passed by and ate the rest of the gnolls, the team interrogates the hideous monstrosity. As Fechin reads his mind, he sees four female humanoid gnolls in a counsel. He sees two groups of gnolls fighting, one of which includes the members of the just-beaten fighters, which fleed as others died in front of them. He sees also the home of the gnolls, somewhere within the realms of the plains and next to an unknown mountain, probably to the west or south from their current location.

The group travels towards the tower, during which they see footmarks half a meter in diameter, probably of two creatures, rain clouds to the east where they came from, a city to the north and a green toxic cloud to the south-east at an unknown distance. They get closer to the tower which seems to be 20 meters in diameter and about 100 meters in height.

\chapter*{Session 4}

We see the tower is made of bones. It's written about a god named Yeenoghu in there.
Kortarr finds out that the bones are all about one-year old. The bones below are more unnaturally bent (but not broken) and fractured then those above them. Some 40-meters above there are one or two skulls with tusks.
There are some gnoll-skulls and there are many bones too big. Some could have belonged to cow-like animals.
The bone isn't as dense above, and the bones are bigger. The width of the tower doesn't differ.
The ground around the tower is dryer than the ground in the vicinity. AS the ground is dry, we can see our own footsteps, but not the footsteps of others. There's strong necromatic magic centred at the tower, and the ground smells. The ground feels dead and it hard to dig through.
The bones are very bright white, as if they were cleaned.

Kortarr, climbing the tower, sees that one of the skulls points towards a town with lights in it. The skull has a similar expression to the cow-like animal that looked at the group earlier. One of its tusks seems to have been cut in half but repaired. He sees also, to the south-west another similar tower to the one he's climbing. There's some symmetry in the bones of the tower. There's at some point a lion-skull pointing at the small green cloud next to the city. There are spine-bones within the tower, and also bones of a giant scorpion. There's another bone tower to the north-west and another tower at the west. There are around 200 kilometers of plains to the west. There's a wall around the city to the north, and there's a river going through the city.
There doesn't seem to be sun-damage on the bones. Around 60-meters tall there are again broken bones and some sharp bones. Kortarr then needs the grip of the red body of the tower. It seems like the body of the tower grew, rather than was build. It feels somewhat magnetic, sticky and stone-like. Kortarr eventually reaches the top of the tower. He sees another tower to the west-north, at some distance.
There are ore humanoid bones at the top, and they aren't bent as those below. There are also shattered and crushed bones at the top.
Kortarr sees something flying next to the green cloud next to the city to the north. He sees no talon marks on the tower, as he would expect at the top of a tower.

The group walks north, towards the river going from the mountain to the north-west to the city on the north-north-east. They hear another thunder-like sound similar to one they heard at the tower. Aio sees a storm around the city and we notice at some point a small town within the green cloud. There seems to be smoke within the green and there are methodical holes in the city walls. The city is some 10 kilometers from the group. Creatures come out of the green cloud and one of them flies towards the group. A creature of size of some 5 meters is coming towards the team and flies in circles above the group. It has a long tail and spikes on its body. 
The creature, apparently a manticore, attacks the group with a barrage of spikes. After trying to fight it, they group decides to escape to the nearby river. As they go under the trees the creature flies away.

The group passes the river and surrounds the city until they reach a breach in the wall. As they reach the breach, they are attacked by less-distorted gnolls. As they flee into the town, something protects them from the attacks of the gnolls. As they enter the town, purple mist follows them, which appears to be a ghost of a hobgoblin, then vanishing into the air.

\chapter*{Session 5}


As the group walks into the city, they see weapons long-left on the ground. They walk towards the north half of the city, seeing wrecked buildings on the way.

The group walks into a stone pantheon, with a shrine in the middle of it. Fechin picks up a staff from next to the shrine as a female ghost of a hobgoblin appears. After some interaction and an offering from Chaataan, the ghost allows the group to their own, asking them to save or help something.

In search for a place to rest, the group passes a building in which Chaataan senses something undead, and a building in which he senses something ethereal or outer-planar.

The group enters a safe-looking building where Aio and Fechin rest, while Chaataan and Kortarr try to fish for food. Fechin looks into Aio's stuff and notices that the magical feather from Aio's hat points west-south. If it points to a static place it would be south-west of the mountain to the west.

As they rest, the team has visions of some spells and creatures. They include giant hyenas, a twisted giant dog with some sort of green bump spilling liquid from it, and something which seems to be a giant elephant of sort.
In the visions there are giant green arrows destroying a building, gnolls fighting, the city wall being destroyed.
It seemed like the occurrences of the nightmares are from approximately 5-15 years ago.

The team goes the get food from the river and later goes to the river in which they see a wrecked ship. Not knowing how to fix it and return to Aio's ship, they team goes to travel into the city.

\chapter*{Session 6}

We reached a shadowfell temple with a rod in it, inside the wall. As Chaataan takes the rod out a shadowfell spirit, which seems unrelated to the origin of the place, appears. We take the rod and go out. Kortarr sees the runes on the rod as reminding movement, instability, innertia and death, interwined with each other.

We get to the ship, fix it and travel towards the sea. Chaataan blows the horn he found in the city and after going out of the darkness which I had cast we see the dead knolls on the shore.

After escaping into the sea and going towards Aio's ship through the direction of the storm, we are chased by three ships that travel strangely fast. One of the ships is large and contains maybe 20 people. The other two are smaller. We pass through the storm and manage to escape from the ships.

We see a small island on the way and eventually get back to Aio's ship by the swamp and rest for about a week.

\chapter*{Session 7}

Looking at the notes I understood that the ghost in the city called us enemies of the gnolls, and that the ghosts helped us because we had previously killed gnolls. The writer says that the rod was part of an arch-lich and experimented on it to try ward off the gnolls by getting energy from the dojo, somewhat successfully

I go outside with the ratadpole for a walk. I am reminded by neothelids, animals of the mindflayers and which by the end of their life-cycles turn out to be giant worm-like monsters. It very much doesn't seem to me like the ratadpole is the same.

We go down to the shore with Aio's frozen bear and unfreeze it. It is furious, shouts in what seems to be grief and attacks Chaataan and Aio before we freeze it again.

A ship, about the size of the Ratadpole (the ship we had found in the city) arrives with a flag on which there's a brown shiny gauntlet. Chaataan recognizes the art as done by an artist from Wakaharu. Chaataan recognizes a person from abroad the ship, a female half-orc named Dolkar, at the age of 17, who lived in the streets of Wakaharu. She calls him by his name and asks about us. He doesn't recognize any of the other four people on the ship. The people on the ship are all young, with the oldest being a female elf, about 20 years of age. There's a friendly-looking dwarf, smiling, a female gnome who seems to be interested about what Chaataan tells about me and who has half-burnt hair, and a plain human (who appears to be the sailor).

I ask the elf, apparently a wood elf whence they came from, but she only replies they came from the south. She goes by the name of Tonal'nan and is recognized by Kortarr as someone who travelled to woods under his guidance. Aio recognizes the dwarf but can't remember from where. Aio discovers from the human that they came from the same village as we did. 

I approach the interested gnome named Deina and tell her about what we saw, apart from those regarding what we took from the city. She says she is interested in such things as a creator who is interested in things might help her in her creations, and reveals two artifacts which she created, apparently an artificer herself.

Aio talks to the human and discovers that they travelled to the south, sailed for two-three days next to mountains and two days near the desert where they saw what seemed to be people on horses. They entered the desert in which they saw a temple with traps and strange creatures who scared them away, maybe mummies. The sea itself was quite calm, and they hired the ship from Wakaharu. It doesn't seem like he is hiding anything.

Chaataan talks with Dolkar who was not in Wakaharu during the time.

Trying to detect magic I see two glowing balls and about 3 smaller objects, mostly with transmutation magic, the human seems to be radiating weak evocation magic, and the Dolkar's short sword seems to have some magical energy in it. Tonal'nan seems to stay too far away, and there's nothing else I manage to notice.
I show the other group the rod and ratadpole to show the people. The dwarf Fervin calls the rod an unholy abomination and warns us about it. He says that it's very strong and corrupting. He says that it may explode when attacked by a necromancer and that it may attract vampires or the sort. He tells me to the the ratadpole away. It appears like they don't plan to stay long near us.
Chaataan brings the stone rod and Ervin doesn't know much about it. He says it's strong but not nearly as strong as my dark rod.
Deina's trap contains poisoned needles and uses a thread as an activation mechanism. There's some sort of transmutation magic preserving the poison. 
Kortarr can't detect what poison it is as there's not enough of it and Deina doesn't want it to be removed.

We go to check the island. As we arrive before morning we see that the light-house isn't working. There's a sunken ship by the island and there are old planks by the shore. The island lain is mountain-like and the shore contains shrubs and grass but no trees whatsoever. Kortarr sees some animals, bats, tortoises et cetera.

We go to the forest in front of the island after Kortarr notices some eyes looking at us. After talking with Chaataan the creature reveals to us and comes a bit towards us. Its skin is green and it wears a cloak of leaves. It seems familiar to me as I've heard about such creatures and was told they don't tend to aggression unless their forests aren't respected.
Chaataan approaches the creature and tells him that we came from across the ocean. The creature says his name is Ong'ko. Chaataan tells him about the rising of the land. Ong'ko says the he's heard of such rumors, that he's a hermit/outcast/exile living alone in the area. He says that there's a large population of firbolgs (which he is one of) in a village in the forest.
He says that the other firbolgs aren't alright, and that he hasn't seen any gnoll for 15 years and doesn't know about twisted gnolls. He says that the hobgoblins were on their side. He has heard about the ruined city, which was about 15 years ago. He knows about the necromancer towers but don't know about them. He asks if we planned on going towards the lighthouse and says that the island is much more dangerous than the plains. Fortunately, those creatures aren't as intelligent. He says that they're giant and flying, and that the uprooted trees we saw were due to those giants. He calls the giant creatures ``Rocs'' which Kortarr knows are giant birds. They don't tend to be aggressive but they are territorial. They aren't very natural (and are magical) and they cause the storms around here.
He says that as he understands there's a dragon in the swamp. He says that the other firbolgs would be amicable towards us if we talk in giant and say we fought the gnolls. He doesn't know about the king of the mountain. He also said that the king of the mountain is a dragon.

\chapter*{Session 8}

We go through the  forest which seems to have some markings of large reptiles on the trees. There seem to be traces on the path, and hooves markings, but that they didn't leave much impact on the woods.
We find a small stream of water, with slight strong smell from it and small fish.
We reach a dam and I see that the ants at both sides have different kinds of magic on them. Those to the north radiate weak of transmutation and evocation magic and those to the south of it radiate necromatic magic.
We hear clashing metal at some point.

We reach a clearing where firbolgs in armour and bows surround us. Chaatan greets them and after a while a female character named Sujita with some herbal construction over her eye tells us to not be afraid. After casting some magic on a box, which seems to be an enchantment area effect, we all hear her voice repeated in our comfortable languages.
She asks us to visit their village and says that their council would like to meet us. As she go, she rides a 4-meter long saddled reptilian creature. As we reach the place, we believe there are a few thousand firbolgs living in there.

At the villae, we see strange big wooden structures, something that looks like training grounds, a few small ponds and fruit trees (which we didn't see on our way). We reach a hall made of wood and some metal and stone. We reach a waiting room.
The female tells me about their history. Their ancestors have been around the forest for hundreds of years, but their current coalition exists four about three, due to conflicts with the gnolls.
The room we enter to looks like part of a court, but not in the courtroom. The female puts the box, which seems a bit dusty, in front of her, and we sit on uncomfortably large chairs in front of a semicircle of firbolgs. The seven firbolgs (not including the female) wear different clothings. Five of them (some males and some females) wear military uniform, quite similar to each other. One of them, a female, looks like a druid and extremely similar to Ong'ko. The seventh one, a bit wider than the rest, looks like a craftsman. Their chairs are better than ours.

Aio greets the firbolgs in some of their local blessings. He then tells them about our journey. They seem suprised by the fact that we came from the east, saying that there is nothing there. Chaataan says there three weeks ago the island appeared in our world, and they say that a long total eclipse also happened in their skies at that time, the same as in the plains. It appeared together with earthquake, which they didn't expect, and many of the birds disappeared. Birds went out of Wakaharu towards other parts of our continent as well, and we didn't see migration of birds when we reached the island.

They didn't travel far, being surrounded by gnolls, monsters, and swamp. They did however have friendship with sea-living creatures who have an underwater city. Some of them were attacked by similar creatures though, during the past year or so.
They say that the large pillars were constructed some 150 years ago quite quickly, and that they don't know by whom. Their newest records of south of the swamp are from about 150 years ago. They don't have records of meeting the king of the mountain and they have heard of cities within the desert, but their latest explorations towards that region showed that those aren't active.
They say that the ants have been fighting each other, and that there's much harmony in the forest. They say that they think the ants don't consist of a hive-mind as strong as the psychic connection of e.g. that of Neogi, legendary creature the leave underground and have power domination powers. They say some people try to use the ants to their advantage.

The council invites us to stay as long as we stay together and with Sujita. That say that we aren't to visit some research area, the main training grounds, and their temple. They would like us to help understand the problems with the sea creatures, and the disappearance of the birds. They show us images of the sea creatures, which seem to be merfolk. The creatures that attacked them seem to be larger anrgier merfolk.

Sujita says that she's the historian of the village. She says that her box is an artifact that was built or given to their people hundreds of years ago. It is their most expensive object. They managed to discuss with the merfolk without using the artifact. There is a small stream going through the ponds of water in the village. Some of them contain fish and the last of them contains a bad smell that seems to be what we smelled in the forest. Sujita mentions that three years ago when the firbolgs united, some of them refused to join and stayed separate in the southern part of the vilage.
North of the village we see a construction area where they build bricks and carpentry. North of that are stacked deployable walls made of wood.

\chapter*{Session 9}

We enter the pub, named Kedai Tingi, where there is a barmaid by the name Sutiono. She asks if we need a place to spend the night and says that there might be such place for us. She tells us that she's worked there since she became blinded. She says that music and playing in Utajan (their forest) were always something done in groups. There are musical instruments in the place. There is a female person smoking and sitting with another person; she has divination magic on her and the person next to her seems to be afraid of the barmaid.
Sujita tells us that the people attacked by the merfolk saw some inanimate objects out of the water towards where they were going. There's a somewhat dormant monster in a cave by the shore.

I approach the table with the smoking person and her friend, and ask them to join us. The woman, Hendra, smokes something given to her by her friend Suritman. She has just past a test to advance to become a member in the clergy. Suritman mentions as part of the conversation that there are monster and tough creatures in the way towards the village to the south. Some creatures in the area don't approve of the union of the firbolgs. He says that a tree south of that village has some interesting animals and spirits in it. He says that the village to south is peaceful.

We go to meet Ongko who helps us breath under water. We get towards the place with the structures that was seen by the firbolgs. I see sculptures of fish within a cave. There are wooden tools in it, not destroyed by the water. It might be a small house, possibly a storage room. There are a few similar caves nearby. As I go up I see Kortarr has found a corpse of a merfolk whose clothes has many pockets. The merfolk is missing part of its abdomen. There are no bite marks, although the water might have erased such traces.

\chapter*{Session 10}

We see in one of the caves drawings of merfolk, fish, and larger scarier humanoids on ships and with weapons, likely tritons. We go down through some sort of corridor. At some point there's a sort of spiral stairway, and there seem to be some sort of fortification. We go down through this 30-meter path and reach a hall. There are trails for a heavy sliding door which is missing.
The trail is a little bit bent and has orange and green corrosion. We can't identify the metal.

In the hall there are wooden and shell-made shelves. There are about 15 shell-made round doors that are missing handles, and open towards us. At the centre of the hall there's a round tribune with place for about a hundred people. Inside it is a 5-meter radius disc for people to stand in.
At the very centre is a metal statue which doesn't seem to have a coherent shape. It has similar corrosion to the door trails.
The doors a somewhat thick, as Chattaan finds out, and the material is quite though. The water in the hall are slightly red and darker than the water outside it.

We manage to enter one of the rooms. It has drawings and statues describing the building of the hall. There are merfolks with expressions in the drawings, and the doors are open. They are very fish-like, more so than human-looking.

Aio enter a room connected to the one we entered. There are fish-bones and stone-tablets with writings in it. It might be a storage room. As we entered the room, I hear an increasing high-pitch metal sound. The tablet described the construction of the place, but I see nothing too interesting. Chattaan manages to detect creatures with their heavy weapons  grinding against the door trails.
There is unholy energy from those creatures which aren't themselves undead.
They enter towards the middle of the hall. We attract them and Kortarr makes a distraction. 

They seem to be the monster merfolks. They're quite large, larger than Chattaan. We beat them after a fight and I interrogate one  of them which we capture. It thinks about being inside the hall, and playing music. It thinks of an underwater city, related to a curse and its cure. As I delve deeper I see it together with other merfolk with torches, then escaping from something that kills its friends. It sees a claw as the dream moves forward. His hands, with which he tries to defend himself, are of another merfolk.

We talk with the merfolks that come out of their hide. We talk to them. They say they don't have means for us to keep breathing underwater. They say that the other city, which I saw in the dream, is on the way to the shore by the Roc island. They call the city Ukuaru. An old merfolk says that Aio and Chattaan are in trouble; they remind him of the merfolk that turned into werefolk, before their transformations. The werefolk started around a month ago, after things partly went above the water.

\chapter*{12}

The merfolk have lost a few dozens to the cursed. They say that managed to delay the curse on some of the  later werefolk, with some herb that also manages to repel those creatures.
They are scarce with these herbs.
Regarding the harpoons of the werefolk, they were crafted by the merfolk during the days they were in the city, as fishing tools.
The city was since evacuated in some sense that's not completely coherent to us. They haven't been in the city around a decade after having lost a large war. Leaving that city was part of the peace agreement. He doesn't seem to want to elaborate on that, having somewhat anti-patriotic opinions.
The war was with some dark creatures of the ocean, or tyrants of the ocean. Aio says that it's a name for the sea Tritons. The old merfolk, named Kersa, teaches Aio and Chaatan how to say they're friendly, in case we arrive. It's ``E'thefau''.

Outside, we are chased by tritons carried by two giant ocean sunfish.
They eventually stop us. They talk with Aio and are worried about Aio's and Chattaan's condition, saying that they can't let them go down to shore. They follow us to allow Kortarr and myself to inform the Firbolgs and ask for their help.

The Firbolgs are happy to hear that the good merfolks are okay. Sujita says the merfolks might have built the lighthouse. She's sad to hear about the curse; she says it sounds like an ancient curse. We go back towards the ship and pass through traces of Ongko. We search for him for his abilities of water-breathing. 

\chapter*{13}

After a rest we plan to go to Ukwahiwu. The bloody tritons leave us alone due to political reasons.

We go underwater and see a giant structure with an hexagonal face on the top of it, of radius about 120-150m. It seems to be made of stone and there are window-like squares in it, which reveal rooms beneath them. They are oriented strangely.
There are weird poisonous plants on the edge of the hexagon.

We travel down into a merfolk city. We pass by an awfully impolite merfolk. We eventually reach a hall with hard-to-read maps and drawings over the doors, depicting all sorts of parts of the island. These include bone-towers, the mountain with the giant door, the Roc island, with more buildings on it. We see a drawing of a small building in the direction of Parlaisat (the ruined city we went through). There is a drawing of a giant octopus-bird creature over the doors.
In the north there are drawings of very evil tritons.

We travel for while, discovering three rooms which seem to contain treasures of the merfolk. Many doors are locked, some of which are reinforced by magic. We escape some more impolite werefolk and eventually capture one merfolk. He seems quite young and mostly like a regular merfolk, although a bit sick.

\chapter*{14}

In the dream, the merfolk works in large room. He goes outside where it's dark and swims very quickly. When I ask about his leader, I see him thinking of a dark cloud surrounded by figures which he seems to recognize, although I don't. I can't find out when he became cursed.

Chaatan knocks out the merfolk and it seems like his eyes are a bit calmer when he's asleep. It reminds me of domination rather than corruption, but it doesn't quite fits that the werefolk are just being controlled.

We travel to the third storage room and find all doors destroyed. Nothing special in there. We go through a strange door in front of the storage room. We continue through a corridor and reach a large dark hall. In it are statues, one of which is of a merfolk reminding us of the creation god which gave us Chaatan's rod.

We get into one of the rooms behind the other seven doors. On one of the desks, there's some text saying that the emergency efforts should be cut down and the some sort of leaders says that everyone should stay calm. It looks like a copy-room and there's some large magical chest which can keep things dry in it. It has glyphs on its side which probably keep it dry. I copy the glyphs into my book.

We go back to the map room. We understand the map better now, and we see a sort of lab above the collapsed corridor and third storage room.

We get into a laboratory with strange lines on the floor, and a collapsed corner in the room. The lines get denser around the collapsed corner, and Chaatan's stone rod helps us understand where the collapsed stones fit.

We try to get back to the second storage room, but get chased out by werefolk.

\chapter*{15}

We go up and update the tritons while we're on the way to Ong'ko. They have a chest with glyphs similar to the ones I copied, but don't understand it well. They don't recognize the creature we met on the way to the continent. They somewhat recognize the kind of metalwork but not the coin itself. They tell us there might be treasure on the Roc island and in a cave by the shore.

Togashi's lieutenant Qu'akk says that everything we mentioned is related to the Far Realms. He says that the creatures there hate each other more than most and that the curse is probably some link to there. 
He doesn't recognize the 5 lines which we saw everywhere. He says that the collapsed corner in the lab must have been a portal, warning us from copying too much. He says that the monorail is probably some link to the Far Realms. He says that the creatures from the Far Realms are usually single-minded and are driven by a specific urge. They have telepathic and magic-detecting abilities. 

We go back to the merfolk city and defeat the monorail (which is a crab-like creature) by sending it back to the far realms through a portal.

\chapter*{16}

While we rest in the area, Aio and Chattaan meet a mercenary ship that originally came from Wakahauru. Their ship isn't well-kept. They saw a steaming mountain to the west, and went through the plains. Didn't give much useful info and said they were on their way back.
They did see caves in the mountains but saw that one can enter only through water which was difficult for them. They also saw a forest and some destroyed villages. They saw some constructions on the entrance to the mountain-pass. The Tritons show Aio and Chattaan a bright star in the east-east-south which flickers inconsistently, with some sort of pattern, about an hour a night.

While looking at the sea to think about the storm, Kortarr and myself see a ship arriving from the south. It has no flag and it passes next to us and sails onward. We see also the flickering stars, which the tritons said started a day or two after we sent to the Far Realms. We understand the the storm is caused by the Rocs. I transcribe the repeating message which repeats 30 times each night. Part of it says ``come quickly'' somewhere in the middle. The whole message is about 20-30 words. It might be some magic cast by a powerful figure. We're not sure it's intended for us or not.

The tritons say that the flickering light is 60-70\% the distance from us to Wakahauru. It doesn't appear to a big distance to the north, probably appearing in some sort of cone from its origin.
We meet Taga, the elvish creature which we met on our way to this place. She's wearing a sort of hood fitting the style of a place called Sarakadia to the north from ten years ago.

She's been waiting for us and asks us for updates. She opens the coin she previously gave us and it reveals sculptures of four cities. They're very far to the north and east. Two of them are on the shore, one of them near the shore and one of them farther away from it. She says the coin was created some 230 years ago. One of them was near Sarakadia. The craftsmanship is very very good.
She gives us some helpful tools for our journey, and a device to let us see us when held and activated. We travel to the west with her sailing near us. She mentioned that the boom above the bone tower was due to the flying of a Roc.

Past the mountain we see a forest where there used to be a city. We see a bone tower to the south-west and a yellow cloud approaching the tower.
There's a canal leading to a pond which was probably by the city.
By the canal we see the ship that Kortarr and I had seen. Aio sees it's a new ship coming from a city to the south of Wakahauro. It's an adventurer ship. It seems that the city disappeared completely.

\chapter*{17}

We sail through the straits to the west. As we enter, the winds are strong and the mist is thick. We see a house between the stone pillars surrounding the area. We stop the ship nearby and see a house on another pillar some 39 meters from the first house. While waiting for Kortarr to use his magic to understand languages, I search for magic in the area and see enchantment magic in the wind. The wind feels musical, and the magic isn't originating from a nearby creature, possibly from another creature or from the place.

Kortarr and Chattaan examine the house, but find nothing very interesting in it. It might have been an emergency or an escape place. Kortarr also saw another taller house in the distance and that there was probably a rope between the pillars, but there are no traces of it. The magic is getting a bit stronger as we stay in the area.

Chattaan goes to the second house. Someone destroyed everything not made of stone in the house. The windows are broken. The chairs and utterly destroyed. There are scratches on the wall. A cellar contains eight beds, larger than in the previous house. Two of the beds are substantially larger and could fit Chattaan were they not destroyed. The text on the walls is written in Hobgoblinoid but Chattaan doesn't transcript it to me. There is a map drawn on the wall. There is a gnoll drawn at the south-east. It doesn't look mutated as the ones we saw but it does look evil. To the east there is a drawing of a whale, probably a metaphorical one, warning of monsters. To the north-west are a few small islands. To the south-west there is a city with a wall, with something written on the wall (but too small to see). To the east-east-south of the city there are forts. There are 4 outposts around the straits, like the one Chattaan visited. There's a river to the right of the forts.

Kortarr then goes to the building to copy the map. I send Sting (my snake) to look at the map and see the arrow to the west-south of the map saying ``county'' and ``Ajensil'' (which is a name of a place). The city is called ``Isemara'' meaning ``great colony''. Below the gnoll there are three words one of which means ``gnoll''.

We are attacked by a harpie who sings in what sounds like Hobgoblin. The sound is magical but we are unaffected and manage to defeat him. We capture him. He's quite young and we capture him. I check the magic in the wind and it's still weak, not likely to have become stronger. Kortarr and Chattaan think that the pillars used to be part of a giant bridge which collapsed for some reason. There has been at least a few hundred years since then, if this is the case.

We travel towards Isemara and see it has an impressive wall and life in it. We approached by a warship about the size of Aio's ship. It has a orange flag with a large triangle on it and a smaller triangle next to it. It has squiggly line on it as if it were text. There is a word saying ``guard'' on it.

They bring us to the city. They all have symbolic tattoos the meaning of which I'm not familiar with. The city walls are about 15 meters tall. The streets aren't very wide, and there are lots of buildings of different kinds. The buildings are mostly 2 or 3 stories each. Almost all of the people in the area have tattoos. Guards at the city entrance have some of their skin revealed, around the tattoos. We are led to the barracks and are told to wait a few minutes. We are led to a relatively small room, with people standing above and around us.

In front of us sits a female hobgoblin and next to her a male hobgoblin, dressed nicely and carrying a small book. He starts singing text from the book for half a minute and then addresses us. He's apparently called Névo Khaldien and is a bard. He asks us where we came from. Aio tells us about that. The man mentions that the flattened city was called Oudfidia. He mentions that the straits were called ``the straits of Moubasharatan''.

Chattaan mentions the eclipse and eruptions in our world, and the man mentions that some event happened here, without elaborating. He mentions Enki's rod and we go through a ceremony to bring it back to their temple. We are greeted by the hobgoblins to stay in Ajensil as we want. We are also invited to their festivities for the return of Enki's rod.
The guard lieutenant Farzané Camran, tells us not to leave the city for now...

\chapter*{18}

We join the hobgoblin festivities. All the adults in the place have tattoos, some of them with up to 5 and some of them crossed with an `X'. Most tattoos are of weapons, and all tattoos are well-done. Some tattoos are of eyes, and some are of other body parts. No two tattoos are exactly identical. None of the tattoos with an almost-closed eye has an `X' on it. It doesn't look like there are any poor people in the festivities, although some seem to be worker-class. There was some selection at the entrance, but it might not be to prevent uninvited people.

Névo says that the people in the city travel through the metropolin Ajensil and rarely further in their empire Mardun Akter Divileti. The all speak the same language in Ajensil and somewhat different dialects in the whole empire. They are mostly the same races, with a few minorities in the country, but not many of them. He says that he has heard of the firbolgs but didn't meet them, and says that the city walls are to prevent the gnoll attacks.

I ask about the tattoos. He says that he doesn't feel qualified to tell us about them in general but can tell about his own tattoos. He has an animal tattoo from his shoulder. Kortarr says it's a dog. It has a strange look on its eyes and isn't very decorated. The dog looks angry. He says that he has abandoned a caravan which had to defend itself, and got the tattoo afterwards.

On his left hand he has a tattoo of a few coins. They don't have many details. They are all broken at their centre. He got the tattoo when he was quite young when he was in charge of cargo and delivery. He left this responsibility and got the tattoo afterwards. 

He has a third tattoo on his nape, of a cat or maybe a caracal, a bit tired, which he got after leaving his parents' home and the duty that was meant for him.

Névo says that the news on our arrival at the city were sent to their capital city of the province and they are waiting their orders.

As we plan to  tell our story of rescuing Enki's rod, some religious figure asks us about the spirit which revealed itself to us, and thanks us for the info.
He knew the person the spirit of which we saw, which came through here to Parlaisat some 60 years ago. She used to be a priest of Enki. He was here when people escaped from the gnolls in Parlaisat and came back to the empire (through the sea, but continued farther into the empire).

We ask about two months ago. There was a moon-eclipse and there were earthquakes. The stars moved. We ask a bit about the stars and he doesn't know enough but says that they have astronomers in the Neisha Ur the capital of the province. There are about 20 provinces in the empire, and Ajensil isn't one of the larger ones. It's about 3/5 of a week to Neisha Ur.
He says that it's about a year to walk the entire empire Mardun Akter Divileti.
They have an Emperor named Bahman Gaazi Divileti in the empire, who reigns for 7 years. He is the son of the previous empress.
We hear that there are elves living somewhere in the area and that someone met tieflings traveling in the south.

We go up stage to perform. Farzané writes a few things and talks with people while we perform. She seems somewhat interested in our performance. The rest of the people look like our story is believable and like they had heard similar stories in the past. The overall vibe is that people are impressed by the story.

A female bugbear approaches us after the show. She isn't dressed as properly as the rest of the crowd and is missing two fingers. She has a large gnoll of an almost-shut eye on the shoulder. Kortarr thinks it looks tired. It looks nicer and is more decorated than Névo's tattoos.
Névo translates for us and says that her name is Bora Nusa and that she works at woodworking for carriages. Her boss Hassim Estasi is under arrest for conspiracy for theft, but she says that he's innocent. She wears an amulet of Enki's. She wants us to help relieve the suspicion from his master and says that she has local money to pay us.

She and Hassim built a fortified carriage for carrying diamonds, and the carriage was later sabotaged with the diamonds stolen. People think that the carriage was sabotaged in advance for the attack to be easier, and blamed Hassim for it. Haassim said on trial that Bora didn't work much on the carriage, so she wasn't blamed for it.

We tell Farzané about the Harpie, showing her illusions of our recollections. Aio notices some people eavesdrop on the conversation. Farzané mentions that the harpies are no longer there and is confused by our findings. She says that people must have hunted them some time ago, while she was still in training.

Aio claims that he woke up in the middle of the night and was approached by a who wanted to secretly notify us of his master's interest in buying our Harpy. He would pay us more for capturing or exterminating the rest of the harpies. Aio and Chaattan go and give them the harpy. They were a bugbear, another bugbear and a hobgoblin. The main bugbear who contacted Aio had a tattoo of a screaming skull. The other two didn't have visable tattoos. The bugbear gave Aio gems worth at least 100 gold for the harpy.

We wake up and go to the temple. We meet Névo and a female goblin. She is about the same age is Aio. She is dressed with impressive clothes decorated with many small gems. She wears a diamond-laid scarf and a shawl...

\chapter*{19}

Névo describes the person as Seda Venat, one of the most famous artists in the city. He says she heard of us from her accomplices who heard us in our show. She wants our help getting a person from a nearby forest, or informing her in case he's dead.
She says that his name is Téro Imben and that he can help her with her [she points at her hand, with a shiny but rusted dagger on it]. She says she shall come with us.

We tell the young lady that we will contact her but have other business to first finish in the city. We visit Bora who tells us, again, about her boss Hassim.
We leave this issue for later and travel with Seda and Névo towards the forest.

On our way we see an old logging camp which was destroyed, seemingly on purpose. The temperature is lower as we travel to the west (towards the forest). The shore contains stones and trees, and is very salty. The forest isn't in particular thick or sparse. It's just a good old forest. Near the other edge of the forest, there's another logging camp which looks more or less the same.

We enter the forest. There seem to be bears, some sort of hives, and Kortarr hears something like deer. How fitting.  We see some foxes who look at us and then keep going, and rabbit-like creatures.

We reach a waterfall going into a small lake. I notice something at the bottom of the lake but can't discern what it is because it's too dark. There's a cavity behind the waterfall which I see through Clairvoyance. There's are drawings carved on the wall on the walls and some fabric, and the cavity is hidden by some other fabric.

We return to rest in the ship for the night before going back to the lake.
We return. Chattaan goes into the lake and brings some dagger and axes from it. We go behind the waterfall. There are drawings of bears, what are probably hobgoblins, a snake, and things of the sort. The drawings look old and don't seem to tell a story. There's an empty wooden box, probably a few years old at most. Nothing magical in the area.
There's something written about purity and love for the forest, and harmony and balance with the animals. It's written in runes reminding of Dwarvish. Névo says it's a language similar to Hobgoblin.

We keep going. We see some berries and strange liken on the trees on stones. The liken is very thick. Aio thinks that some of the berries are poisonous. Chattaan sees something moving up the river, not too large, but it's too far to see what it is.

\chapter*{20}

Aio climbs a tree. He sees some things move in the tree tops, but he doesn't see enough to give details. He sees some creatures moving and a cat.

We enter the cave where there is a giant boulder blocking a passage. I send Sting through which I see a green light. He advances there and senses something strong, but then disappears. :(

The cat meows at the exit and as we exit we see some apes and Tero. He doesn't want want to come back to the city with Seda to help her cross the tattoo. After some convincing, he decides to come with us in three days.

We go to the city in the meanwhile. Aio and Chattaan buy me some incense and herbs for my spells. I go with Kortarr to the book publisher, as he wants to publish his maps and notes.

Aio says they met a female wizard from Réye Mikhadia Yabra, a wizard guild that exists in the area. They've been looking for us. She has abjuration runes on her hands...

\chapter*{21}

The wizard speaks ancient Dwarfish. She wanted to interview the four of us in name of the wizard association and in name of a central administration. Her name is Myransa Bilasat.
Aio and Chattaan then go to explore the local cuisine.
We travel through the market and buy a few things.

We then visit the tattoo authority of the city. He explains about the tattoos. The local wizards have their set of tattoos, people can ask for their own tattoos. He has just decided that two people who fought with each other shall have a tattoo of a bull, to mark their rage.
He says that the city walls have ``don't let down your guard'' written on them. The council of Ajensil has ``don't forget thy duties'' on them. People call him by the name Duvmeji.

He explains that 374 and 142 years ago many parts of the empire were destroyed by gnolls, hence the number of guard in the area. He says that ``Duvmeji'' means tattoo-maker originally and that it turned out to also mean ``adjudicator'' of sorts.

We go to meet Myransa in the guard hall. There are two tables next to each other in the room. She has read about us. She wants to ask us about our magical abilities, in order to catalogue us and pass down the information to their association. They're in charge of the organization and supervision of magic in the area in the past hundreds of years. She asks us to give her information ``or else''. She also shows us her book and explains that she studies defensive structures, hence her knowledge in Dwarvish.
Her organization defended the empire from the technomagis hundreds of years ago, after which the organization was quite large. Since that it has been reducing in size somewhat.

We explain about our magic and Myransa says that some of the information will be sent to Shaßen, the head of Ajensil. We give us more information about our continent. We then ask about the techno-mages. She says that we're during the fifth era, where each era ends with wars and outrages. After the fourth one it was decided that bugbears aren't allowed to live on their own, or own lands. The third era ended with a war against the techno-mages: an organization who melded science and magic, made out mostly of goblins, who wanted to conquer the continent. The war had 70\% casualties out of the whole population. Myransa says that it's known there are no more technomages left, but it might not be true. Since then, goblins aren't allowed to construct tools. During the second era, charismatic hobgoblins started a war in the area which resulted in them conquering the continent. Since then, hobgoblins aren't allowed to give speeches. The first era ended with a gnollish occupation of most of Mardun Akter Divileti. The people managed to stop the gnolls at the emperor's door, together with help from people from Sardiss --- the southern empire. The bone towers appeared during the first era. She says that we might find historians, biologists etc. in Neisha Ur, the centre of Ajensil.

\chapter*{22}

We go to look at the carriage. We see that the left wheel on the back has been shattered, without much damage to the parts next to it. We enter the police station where there are two people talking and one writing. It's a large hall from which one can see the the carriages.

We talk with Hassim Estasi next to his cells. He says that the carriage was ordered by a transportation subsidiary for gem miners. Bora was supposed to join the miners in the carriage but didn't eventually do so because the roads are dangerous and due to other work.

We go to talk with Bora. She said the Hassim talked with her a day before she was about to join the carriage. He said that he is afraid to lose her and that it will be dangerous; he then took extra work as excuse for her not to go.
She comes with us to Hassim's lawyer (Almoz Mariú) which brings us to the carriage together. Chattaan and Bora look at the carriage.

The carriage doesn't have an inner stopping mechanism, and could be stopped by outer devices carried on it. Bora says that it is done this way for transportation services to make stopping more difficult, in case of robbery attempts.
Almaz says that before the job, Hassim met Hamad Muratt, an army officer who worked in logistics in a garrison in the area.

We go out to parties and Chattaan starts a fight. Some bugbear attacks him but escapes. I might recognize him later.

\backmatter
\end{document}